Supplementary Material

### 2019-12-10 papers/ACL2020/experiments.tex

Given the entry-level naming data from ManyNames which extends the \arbitrary naming data from \vg, we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
% found in the verification data in Section \ref{sec:verification}.
%We leave modeling experiments that take into account other possible names of objects for future work.

>>>>

Given the entry-level naming data from \mn which extends the \arbitrary naming data from VisualGenome (\vg), we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
% found in the verification data in Section \ref{sec:verification}.
%We leave modeling experiments that take into account other possible names of objects for future work.
